Gradual Soundness: Lessons from Static Python

### 2021-12-20 pj-7.1/paper.tex
pj: checkpoint, split non-highlights into other secs

@@

@@

\subsubsection{Non-Highlights / Restrictions}

The \SP{} type system excludes include some features.
Each of the following is low priority for the team; that said, they are
ordered below rougly from most important (soonest to be implemented) to least.

\begin{itemize}
  \item \emph{Concrete Parameterized Classes}.
    Except for a handful of built-in types,
    parameterized classes are enforced only with shallow checks.
    In the near future, these classes will gain concrete versions
    for programmers to opt-in to.

  \item \emph{Callable Types, First-Class Classes}.
    The Instagram codebase rarely uses first-class functions, classes, or objects.
    Thus there is little need for either a \code{Callable} type to describe functions
    or first-class types for objects.
    When such values do appear, \SP{} assigns the dynamic type and spot-checks their
    uses.
    For example, every application of a first-class function gets wrapped in a check
    if the context expects a certain type.

  \item \emph{Method Overloading}.
    Methods cannot be overloaded.
    Each combination of a class and a name can refer to at most one method.
    This behavior comes from Python.

  \item \emph{Multiple Inheritance}.
    Multiple inheritance is not supported in a typed way.
    \Cref{s:impl} discusses this point further.

  \item \emph{Strong overrides}.
    Methods and fields may be overridden, but only with values of the same type.
    % In fact, \SP{} compiles fields using Python slots
    % declarations (\code{\_\_slots\_\_}).
    %
    % NOTE __ (dunder) methods may be overridden e.g. __getattribute__,
    % but the normal field access syntax skips any overrides (o.f)

  \item \emph{Recursive Types}.
    \SP{} does not support recursive types.
    Neither does Pyre or mypy.
    %% demand seems low ... baffling
    %% mypy = https://github.com/python/mypy/issues/731
    %% nothing in pep 484 = https://www.python.org/dev/peps/pep-0484/
\end{itemize}

>>>>

%% TODO
%  \item \emph{Concrete Parameterized Classes}.
%    Except for a handful of built-in types,
%    parameterized classes are enforced only with shallow checks.
%    In the near future, these classes will gain concrete versions
%    for programmers to opt-in to.

@@

- static -> static overrides restricted, must be compatible
- static -> dynamic overrides wrapped, in vtable
- dyn -> stat ditto?

XX 
%  \item \emph{Method Overloading}.
%    Methods cannot be overloaded.
%    Each combination of a class and a name can refer to at most one method.
%    This behavior comes from Python.
%
%  \item \emph{Multiple Inheritance}.
%    Multiple inheritance is not supported in a typed way.
%    \Cref{s:impl} discusses this point further.
%
%  \item \emph{Strong overrides}.
%    Methods and fields may be overridden, but only with values of the same type.
%    % In fact, \SP{} compiles fields using Python slots
%    % declarations (\code{\_\_slots\_\_}).
%    %
%    % NOTE __ (dunder) methods may be overridden e.g. __getattribute__,
%    % but the normal field access syntax skips any overrides (o.f)

@@

%  \item \emph{Callable Types, First-Class Classes}.
%    The Instagram codebase rarely uses first-class functions, classes, or objects.
%    Thus there is little need for either a \code{Callable} type to describe functions
%    or first-class types for objects.
%    When such values do appear, \SP{} assigns the dynamic type and spot-checks their
%    uses.
%    For example, every application of a first-class function gets wrapped in a check
%    if the context expects a certain type.
%
%  \item \emph{Recursive Types}.
%    \SP{} does not support recursive types.
%    Neither does Pyre or mypy.
%    %% demand seems low ... baffling
%    %% mypy = https://github.com/python/mypy/issues/731
%    %% nothing in pep 484 = https://www.python.org/dev/peps/pep-0484/
